%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Working Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Research Engineer Intern} % Job title
{Nethermind} % Organization
{London, England (Remote)} % Location
{June. 2024 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Research and development on FRIDA which is DAS using FRI.}
\item {Research on based rollups and preconfirmations.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Undergraduate Research Intern} % Job title
{Seoul National University Virtual Machine \& Optimization Lab} % Organization
{Korea} % Location
{Feb. 2024 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working as an intern researching blockchain core.}
\item {Will begin my Integrated Master's and Ph.D studies in September 2024.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Developer Relations} % Job title
{XRPL Korea} % Organization
{Seoul, Korea} % Location
{June. 2023 - Sep. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed DEX platform on XRPL.}
\item {Researched and developed WASM contract on XRPL.}
\item {Made an technical documentation for Korean XRPL developers.}
\item {Technical sessions on several meetups.}
\item {Provided technical support for the XRPL developers.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Smart Contract \& Backend Developer} % Job title
{Web3Mon} % Organization
{Korea} % Location
{Feb. 2023 - May. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed smart contracts(programs) using Rust for Solana.}
\item {Maintained and developed Rust backend server.}
\item {Conducted research on the novel cross-chain implementation using virtual state channel.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Quantitative Developer} % Job title
{Contract in Person} % Organization
{Remote} % Location
{Oct. 2021 - Jan. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Algorithmic Trading:}
\begin{itemize}
  \item {Developed trading algorithms using technical analysis and AI.}
  \item {Handled large and performance-sensitive data pipeline.}
\end{itemize}
\item {DEX Arbitrage:}
\begin{itemize}
  \item {Conducted research on various MEVs.}
  \item {Developed a cross-DEX, cyclic arbitrage bot using flash swap.}
\end{itemize}
\item {AUM \$400k}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
