%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Honors \& Awards}

%----------------------------------------------------------------------------------------
%	INTERNATIONAL SUBSECTION
%----------------------------------------------------------------------------------------

\cvsubsection{International}

%------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Top Quality Prize, Best Use of Subgraph}
{Chainlink Constellation Hackathon}
{Online}
{Dec. 2023}
{
\begin{cvitems}
\item {Crosschain Lending Protocol}
\item {Implemented crosschain functionalities with CCIP(crosschain interoperability protocol).}
\item {Used DID, graph, oracle services.}
\end{cvitems}
}

\cventry
{Defi Track 3rd Prize}
{Viction Horizon Hackathon}
{Online}
{Dec. 2023}
{
\begin{cvitems}
\item {Delta Neutral Stablecoin using Perpetual DEX.}
\item {Used Layerzero for crosschain support.}
\item {Used VRC-25 for native gas paymaster usage.}
\item {4 days full-sponsored tour to Vietnam hosted by Coin98.}
\end{cvitems}
}

\cventry
{Grand Prize} % Award
{XRPL Summer Hackathon | Ripple} % Event
{Online} % Location
{Aug. 2023} % Date(s)
{
\begin{cvitems}
\item {Implemented concentrated liquidity pool.}
\item {Used XRPL hooks which is a Web Assembly based smart contract on XRP Ledger.}
\end{cvitems}
}

\cventry
{Polygon Track Prize} % Award
{Ethereum Global Tokyo Hackathon} % Event
{Tokyo, Japan} % Location
{April. 2023} % Date(s)
{
\begin{cvitems}
\item {Federated learning on public blockchain.}
\item {Implemented p2p AI learning protocol.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

%----------------------------------------------------------------------------------------
%	DOMESTIC SUBSECTION
%----------------------------------------------------------------------------------------

\cvsubsection{Domestic}

%------------------------------------------------

\begin{cventries}
    

%------------------------------------------------

\cventry
{1st Place} % Award
{Yonsei Computer Science Graduation Project Exhibition} % Event
{Yonsei University, Korea} % Location
{June. 2023} % Date(s)
{
\begin{cvitems}
\item {Data NFT marketplace.}
\item {Process the private data batch into anonymous data set and make it as a NFT for easy usage and incentives.}
\item {Built with Hyperledger Fabric.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}