%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Co-founder \& Lead Engineer} % Job title
{XRPL Swap (DEX Project on XRP Ledger)} % Organization
{Korea} % Location
{Aug. 2023 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Lead Engineer on Decentralized Exchange Platform at XRP Ledger.}
\item {Architected and designed core concepts, including novel tokenomics for the DEX.}
\item {Represented XRPL Swap at the KBW side event "XRP Ledger XCESS", pitching the project.}
\item {Secured 1st prize at the Ripple Hackathon for implementing concentrated liquidity using xrpl hooks.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Developer Relations, XRP Ledger Korea} % Job title
{Catalyze-Research} % Organization
{Seoul, Korea} % Location
{Jul. 2023 - Sep. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Curated and formulated a comprehensive developer curriculum and documentation tailored for Korean XRP Ledger developers.}
\item {Anchored the developer session at the XRP Ledger developer meetup.}
\item {Provided technical support for businesses seeking to incorporate XRP Ledger into their services.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Contract \& Backend Developer} % Job title
{Web3Mon (Web3 Initiative)} % Organization
{Korea} % Location
{Feb. 2023 - Apr. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Crafted and deployed smart contracts using Rust for the Solana blockchain.}
\item {Maintained backend server and conducted research on optimizing virtual state channels.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Quantitative Developer} % Job title
{Contract in Person} % Organization
{Remote} % Location
{Oct. 2021 - Jul. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Algorithmic Trading:}
\begin{itemize}
  \item {Conceptualized, designed, and instituted trading algorithms leveraging technical analysis and machine learning methodologies.}
  \item {Performed continuous monitoring and fine-tuning of trading bots, adapting to market dynamics.}
\end{itemize}
\item {DEX Arbitrage:}
\begin{itemize}
  \item {Conducted research on various MEVs, leading to enhanced arbitrage strategies.}
  \item {Developed a cross-DEX arbitrage bot.}
\end{itemize}
\item {Managed \$400k+ in client assets.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
