%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Extracurricular Activity}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Researcher} % Affiliation/role
{Decipher} % Organization/group
{Seoul National University, Korea} % Location
{Sep. 2023 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {A member of Decipher, a blockchain academic club at Seoul National University.}
\item {Technical research and sessions about various topics of blockchain.}
\item {Team Opensource Warriors}
\begin{itemize}
  \item {Contributed to ERC-6900 github and Alchemy team.}
  \item {Conducted research and made a simulation model for LVR minimization method on AMM DEX.}
\end{itemize}
\item {ZK Research Team}
\begin{itemize}
  \item {Conducted various research on ZKP and rollup architectures.}
  \item {Made PoC level implementation of MSM computing network for ZKP using gRPC.}
\end{itemize}
\item {Held weekly session about the "Future Bank" and published the research on Medium.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Tech Lead \& Board Member} % Affiliation/role
{Blockchain at Yonsei} % Organization/group
{Yonsei University, Korea} % Location
{Sep. 2022 - Aug. 2023} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Completed two semester activity of Blockchain at Yonsei, a blockchain academic club based on Yonsei University.}
\item {Drove research initiatives on emerging topics in blockchain and web3 technologies.}
\item {Held 2 hours sessions about Solidity smart contracts for 6 weeks as a lecturer.}
\item {As a board member, I have structured the semester curriculum and presented three blockchain sessions for the regular session.}
\item {Conducted research on MEV and made arbitrage bot using cyclic arbitrage method on DEX.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Member} % Affiliation/role
{Morgorithm (Algorithm Club at Yonsei University)} % Organization/group
{Yonsei University, Korea} % Location
{Mar. 2020 - Mar. 2022} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Solved and learned algorithm problems in depth and improved coding skills.}
\item {Participated Morgorithm algorithm camp, studied various in-depth algorithms.}
\item {Participated ICPC Sinchon, which is an algorithm competition}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
